\LARGE \bf ***

### 2020-09-22 icra-2021.tex
fixing text in the Introduction (yes, still in the Introduction)

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy, with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying, along with strictly limited energy budgets. Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory in Mei.~et.~al.~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots in Sadrpour.~et.~al.~\cite{sadrpour2013mission,sadrpour2013experimental}.

The algorithm accounts for the energy due to the path similarly to Met~et.~al. but includes the computations in a broad mission planning setting, like the one in Sadrpour~et.~al. It adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. It ideally accounts for a mission extension by adapting both QoS and TEEs as the UAV flyes and its batteries drain. Firstly, the algorithm adapts QoS requiring the UAV to comprise robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters. Secondly, it adapts TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption. The algorithm selects the controls (QoS and TEEs) dynamically using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.

>>>>

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets. Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that overcomes the traditional planning and addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
The algorithm inspires notably by the technique of coupling the energy due to the computations performed and trajectory traveled, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

The proposed algorithm adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters. It optimizes TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption. The algorithm selects the controls (the QoS and TEEs) using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.
